User-level Grid Monitoring with Inca 2

### 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
template changes for final version to be printed
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6855 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{dblfloatfix}
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{times}
\usepackage{url}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
% takes away page numbers
\pagestyle{empty}

% some unnecessary whitespace still -- these suggestions from
% http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/squeeze.html
\renewcommand\dblfloatpagefraction{.95}
\renewcommand\dbltopfraction{.95}
\renewcommand\bottomfraction{.95}
\renewcommand\textfraction{.05}   
\setcounter{totalnumber}{50}
\setcounter{dbltopnumber}{50}
\setcounter{bottomnumber}{50}

%------------------------------------------------------------------------- 
\begin{document}

@@

\author{Shava Smallen, Kate Ericson, Jim Hayes, Catherine Olschanowsky \\
San Diego Supercomputer Center\\ University of California, San Diego\\ 
9500 Gilman Drive, La Jolla, CA 92093-0505, USA\\ 
\{ssmallen,kericson,jhayes,cmills\}@sdsc.edu\\
}

\maketitle
\thispagestyle{empty}

@@

%------------------------------------------------------------------------- 
\Section{Introduction}
\label{intro}

@@

% What types of Grid monitoring are around and what the limitations are
One approach to monitoring Grids, used by tools such as
MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
display data from existing cluster or system administrator monitoring tools
such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
resources where low-level host statistics and queue information can be
examined.  This type of monitoring information is useful for showing the
utilization of Grid resources, but it does not provide the type of
high-level monitoring needed to detect user problems, such as incompatible
software versions, within the Grid infrastructure.

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
from a generic, impartial user's perspective.  The goal of user-level monitoring is 
to detect and fix Grid infrastructure problems before users notice them -- 
user complaints should not be the first indication of Grid failures.  
In our view, successful user-level Grid monitoring needs to include
these features:

@@

%------------------------------------------------------------------------- 
\Section{Inca 2 Features}

@@

%------------------------------------------------------------------------- 
\Section{Inca 2 Architecture}

@@

\SubSection{Reporters}

@@

\SubSection{Reporter Repositories}

@@

\SubSection{Inca administration tool (incat)}

@@

\SubSection{Agent}
\label{agent}

@@

\SubSection{Reporter Manager}
\label{rm}

@@

\SubSection{Depot}

@@

\SubSection{Data Consumer}

@@

\SubSection{Security}
\label{security}

@@

\SubSection{Coordinating Inca Deployments}

@@

\Section{Use Cases}
\label{usecases}

\SubSection{TeraGrid}

@@

\SubSection{GrASP}
\label{grasp}

@@

\SubSection{Other Uses}

@@

%------------------------------------------------------------------------- 
\Section{Future Work}

@@

%------------------------------------------------------------------------- 
\Section{Summary}

@@

%------------------------------------------------------------------------- 
\Section{Acknowledgements}

@@

%------------------------------------------------------------------------- 
\bibliographystyle{latex8}
\bibliography{paper}

>>>>

\documentclass{sig-alternate}
\usepackage{epsfig}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{url}

%------------------------------------------------------------------------- 
% Begin patch area for accents in 'Author Block' area - may be needed by
% some authors / but not all
\DeclareFixedFont{\auacc}{OT1}{phv}{m}{n}{12}   % Needed for "Author Block" accents - Patch by Gerry 3/21/07
\DeclareFixedFont{\afacc}{OT1}{phv}{m}{n}{10}   % Needed for "Author Block" accents in the affiliation/address line - Patch by Gerry 3/21/07
%-------------------------------------------------------------------------

\begin{document}

\conferenceinfo{HPDC'07,} {June 25--29, 2007, Monterey, California, USA.}
\CopyrightYear{2007}
\crdata{978-1-59593-673-8/07/0006}

@@

\numberofauthors{1}

\author{
\alignauthor
Shava Smallen, Kate Ericson, Jim Hayes, Catherine Olschanowsky \\
\affaddr{San Diego Supercomputer Center} \\ 
\affaddr{University of California, San Diego} \\ 
\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
\email{\{ssmallen,kericson,jhayes,cmills\}@sdsc.edu}\\
}

\maketitle

@@

% A category with the (minimum) three required fields
\category{C.4}{Performance Of Systems}{Performance attributes, Reliability,
availability, and serviceability}

\terms{Performance, Reliability, Verification}

\keywords{User-level Grid monitoring, Grid monitoring, TeraGrid}

%------------------------------------------------------------------------- 
\section{Introduction}
\label{intro}

@@

% What types of Grid monitoring are around and what the limitations are
One approach to monitoring Grids, used by tools such as
MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
display data from existing cluster or system administrator monitoring tools
such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
resources where low-level host statistics and queue information can be
examined.  This type of monitoring information is useful for showing the
utilization of Grid resources, but it does not provide the type of
high-level monitoring needed to detect user problems, such as incompatible
software components, within the Grid infrastructure.  Industry monitoring
tools are also available such as IBM Tivoli Monitoring~\cite{tivoli} and
Microsoft Operations Manager~\cite{mom}, which monitor and manage large
networks of services.  However, these tools depend on proprietary software and
are targeted to a single administrative domain, which is unsuitable for Grid
systems that span multiple administrative domains.

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
from a generic, impartial user's perspective.  The goal of user-level monitoring is 
to detect and fix Grid infrastructure problems before users notice them by
notifying site system administrators and providing them with the error details -- 
user complaints should not be the first indication of Grid failures.  
In our view, successful user-level Grid monitoring needs to include
these features:

@@

%------------------------------------------------------------------------- 
\section{Inca 2 Features}

@@

%------------------------------------------------------------------------- 
\section{Inca 2 Architecture}

@@

\subsection{Reporters}

@@

\subsection{Reporter Repositories}

@@

\subsection{Inca administration tool (incat)}

@@

\subsection{Agent}
\label{agent}

@@

\subsection{Reporter Manager}
\label{rm}

@@

\subsection{Depot}

@@

\subsection{Data Consumer}

@@

\subsection{Security}
\label{security}

@@

\subsection{Coordinating Inca Deployments}

@@

\section{Use Cases}
\label{usecases}

\subsection{TeraGrid}

@@

\subsection{GrASP}
\label{grasp}

@@

\subsection{Other Uses}

@@

%------------------------------------------------------------------------- 
\section{Future Work}

@@

%------------------------------------------------------------------------- 
\section{Summary}

@@

%------------------------------------------------------------------------- 
\section{Acknowledgements}

@@

%------------------------------------------------------------------------- 
\bibliographystyle{abbrv}
\bibliography{paper}
